BACI of biomass change for VOCC source cells for all years

### 2019-10-02 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
filter NA columns to allow match to run; saving temperature-based matches

---
title: "BACI of biomass change for VOCC source cells for all years"
author: "Philina English"
date: `r Sys.Date()`
output: html_document
params: 
    species: "Pacific Ocean Perch" 
    region: "both odd year surveys"
    age: "imm"
    biomass_threshold: "25"
    climate: "do"
    threshold: 0.25
---

@@

all_vectors$var_1_min <- lower_thresholds[1]
all_vectors$var_2_min <- lower_thresholds[2]
all_vectors$var_1_max <- lower_thresholds[1]
all_vectors$var_2_max <- lower_thresholds[2]
```

@@

alldata <- rbind(source_biomass, control_biomass)
alldata <- mutate(alldata, treat = ifelse(cell_type == "source", 1, 0)) %>%
  select(-var_2_min, -var_2_max, -mean_target_X, -mean_target_Y) %>%
  rename(vect_dist = distance)
alldata$treat <- as.factor(alldata$treat)

# alldata
# })
```

@@

@@

if (climate == "temperature") {
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string, age))
}
if (climate == "temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold, "/", max_string, "/", age, "/vocc-", climate_string, "-", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"))
}

>>>>

---
title: "BACI of biomass change for VOCC source cells for all years"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Pacific Ocean Perch" 
    region: "both odd year surveys"
    age: "imm"
    biomass_threshold: "25"
    climate: "temperature"
    threshold: 0.25
---

@@

all_vectors$var_1_min <- lower_thresholds[1]
all_vectors$var_2_min <- lower_thresholds[2]
all_vectors$var_1_max <- upper_thresholds[1]
all_vectors$var_2_max <- upper_thresholds[2]
```

@@

alldata <- rbind(source_biomass, control_biomass)
alldata <- mutate(alldata, treat = ifelse(cell_type == "source", 1, 0)) %>%
  select(-mean_target_X, -mean_target_Y) %>%
  rename(vect_dist = distance)
alldata$treat <- as.factor(alldata$treat)

if(is.na(alldata$var_1_max[2])) {
  alldata <- alldata %>% select(-var_1_max)
}
if(is.na(alldata$var_1_min[2])) {
  alldata <- alldata %>% select(-var_1_min)
}
if(is.na(alldata$var_2_max[2])) {
  alldata <- alldata %>% select(-var_2_max)
}
if(is.na(alldata$var_2_min[2])) {
  alldata <- alldata %>% select(-var_2_min)
}
# alldata
# })
```

@@

# alldata[ , colSums(is.na(alldata)) == 0]
# alldata <- alldata %>% select(-var_1_min)

@@

if (climate == "temperature") {
  dir.create(file.path("data/_all", climate_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string, age))
}
if (climate == "temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold, "/", max_string, "/", age, "/vocc-", climate_string, "-", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"))
}
